---
title: "tolnay news link"
output: html_document
date: "2023-11-01"
---
### Wells matching GA news and GA Tolnay

```{r setup, include=FALSE}

#install.packages("here")
#here::here()
library(tidyverse)
library(tidyr)
#install.packages("ggmap")
library(ggmap)
#install.packages("geosphere")
library(geosphere)
library(janitor)
#install.packages('scales')
library(scales)

```


```{r}

tolnay_beck <- read.csv("../data/bailey_beck_lynching_list_8_1_2022.csv") %>%
  as.data.frame()

tolnay_beck <- janitor::clean_names(tolnay_beck)



lynch_updated <- read_csv("../data/lynch_geocoded_10.8.csv")

# make less ugly
lynch_updated <- lynch_updated %>%
  clean_names()

```


```


```{r}
#How many GA papers that we coded could have covered Tolnay-Beck listed lynchings
ga_tolnay <- tolnay_beck %>% 
  filter(lynch_state =="GA") %>% 
  mutate(date = paste(month,day,year, sep = "/")) %>% 
  mutate(tolnay_date = as.Date(date, "%m/%d/%Y")) %>% 
  select(status, tolnay_date, year, month, day, name, alt_name_1, lynch_county, lynch_state, method_of_death, accusation)
#685 from 1865-2001

ga_news <- lynch_updated %>% 
   filter(newspaper_state_code == "GA") %>%
   mutate(date = as.Date(date, "%m/%d/%Y")) %>% 
   mutate(year = lubridate::year(date), 
                month = lubridate::month(date), 
                day = lubridate::day(date)) %>% 
  select(date, newspaper_name, newspaper_state_code, year, month, day, decade, city_lynch, state_lynch, in_state, border, total_words, file_id, url)
#66 obs 1881-1920


# Create a sequence of dates for 15 days after date1
ga_news$date_seq <- lapply(ga_news$date, function(x) seq(as.Date(x), by = "day", length.out = 16))

# Unnest the data frame
library(tidyr)
ga_news <- unnest(ga_news, cols = c(date_seq))

ga_tolnay_news <- ga_tolnay %>% 
  inner_join(ga_news, by=c("tolnay_date"="date_seq")) %>% 
  rename(city_newspaper_report = city_lynch, tolnay_year = year.x, tolnay_month = month.x, tolnay_day = day.x, news_year = year.y, news_month = month.y, news_day = day.y, news_date = date) %>% 
  select(tolnay_year, tolnay_date, news_date, name, lynch_county, newspaper_name, news_date, news_day, city_newspaper_report, state_lynch, total_words, file_id, url, alt_name_1, method_of_death, accusation, decade) %>% 
  filter(state_lynch =="GA") 

#3 cases where GA papers covered lynchings on the Tolnay list
#My broader join showed 20 obs where GA newspapers match the Tolnay List by year and month. See below


#Notes from earlier method

# #This is sort of an ugly match. Just year and month. A better would be to match 
# ga_tolnay_news <- ga_tolnay %>% 
#   inner_join(ga_news, by=c("year", "month")) %>% 
#   rename(city_newspaper_report = city_lynch, tolnay_day = day.x, news_day = day.y) %>% 
#   select(year, month, tolnay_day, name, lynch_county, newspaper_name, date, news_day, city_newspaper_report, state_lynch, total_words, file_id, url, alt_name_1, method_of_death, accusation, decade) %>% 
#   filter(state_lynch =="GA") 

#20 obs where GA newspapers match the Tolnay List by year and month. Further filtering needed

#filter so the news follows tolnay
#ga_tolnay_news <- ga_tolnay_news[ga_tolnay_news$news_day <= ga_tolnay_news$tolnay_day, ]
#6 cases where GA papers could have covered a lynching listed in tolnay and beck  
```


```{r}
#How many GA papers that we coded could have covered Tolnay-Beck listed lynchings
ga_tolnay <- tolnay_beck %>% 
  filter(lynch_state =="GA") %>% 
  select(status, year, month, day, name, alt_name_1, lynch_county, lynch_state, method_of_death, accusation)
#685 from 1865-2001

ga_news <- lynch_updated %>% 
   filter(newspaper_state_code == "GA") %>%
   mutate(date = as.Date(date, "%m/%d/%Y")) %>% 
   mutate(year = lubridate::year(date), 
                month = lubridate::month(date), 
                day = lubridate::day(date)) %>% 
  select(decade, date, newspaper_name, newspaper_state_code, year, month, day, city_lynch, state_lynch, in_state, border, total_words, file_id, url)
#66 obs 1881-1920

ga_tolnay_news <- ga_tolnay %>% 
  inner_join(ga_news, by=c("year", "month")) %>% 
  rename(city_newspaper_report = city_lynch, tolnay_day = day.x, news_day = day.y) %>% 
  select(year, month, tolnay_day, name, lynch_county, newspaper_name, date, news_day, city_newspaper_report, state_lynch, total_words, file_id, url, alt_name_1, method_of_death, accusation, decade) %>% 
  filter(state_lynch =="GA") 
#20 obs 

ga_tolnay_news <- ga_tolnay_news[ga_tolnay_news$news_day <= ga_tolnay_news$tolnay_day, ]
#6 cases where GA papers could have covered a lynching listed in tolnay and beck  



ga_tolnay_news


```
